On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 paper.tex
Enumitem
Added
wrapfig
added
Reorganization paper.tex

@@

@@

@@

\section{Case of arity $1$}\label{sect:arity1}

\input{arity1}

\section{Case of delay $1$}\label{sect:delay1}
\input{tt_intro}
\input{tt_theorem}

>>>>

\usepackage{enumitem}

@@

\usepackage{wrapfig}

@@

As a result of independent significance, we show that increasing the delay from 1 to 2 enables an oritatami system to yield a conformation of quadratic length in $n$ as long as 5 types of beads are available.

@@

\section{Quadratic lower bound for delay 2, arity 1}\label{sect:lower}

\input{arity1pyramid}

%\section{Case of arity $1$}\label{sect:arity1}

%\input{arity1}

%\section{Case of delay $1$}\label{sect:delay1}

\section{Upper bounds for delay 1 or arity 1}

\input{arity1upper}
\input{tt_intro}
\input{tt_theorem}
